Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-13 Paper.tex

\begin{description}
\item[parentHash]\linkdest{parent_Hash_H__p_def_words}{} The Keccak 256-bit hash of the parent block's header, in its entirety; formally $H_{\mathrm{p}}$.
\item[ommersHash] The Keccak 256-bit hash of the ommers list portion of this block; formally $H_{\mathrm{o}}$.
\item[beneficiary]\linkdest{beneficiary_H__c}{} The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_{\mathrm{c}}$.
\item[stateRoot] The Keccak 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_{\mathrm{r}}$.
\item[transactionsRoot] The Keccak 256-bit hash of the root node of the trie structure populated with each transaction in the transactions list portion of the block; formally $H_{\mathrm{t}}$.
\item[receiptsRoot]\linkdest{receipts_Root_def_words}{} The Keccak 256-bit hash of the root node of the trie structure populated with the receipts of each transaction in the transactions list portion of the block; formally $H_{\mathrm{e}}$.
\item[logsBloom]\linkdest{logs_Bloom_def_words}{} The Bloom filter composed from indexable information (logger address and log topics) contained in each log entry from the receipt of each transaction in the transactions list; formally $H_{\mathrm{b}}$.
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_{\mathrm{d}}$.
\item[number]\linkdest{block_number_word_def_H_i}{} A scalar value equal to the number of ancestor blocks. The genesis block has a number of zero; formally \hyperlink{block_number_H__i}{$H_{\mathrm{i}}$}.
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_{\mathrm{l}}$.
\item[gasUsed]\linkdest{block_gas_used_H__g}{} A scalar value equal to the total gas used in transactions in this block; formally $H_{\mathrm{g}}$.
\item[timestamp]\linkdest{block_timestamp_word_def_H__s}{} A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally \hyperlink{block_timestamp_H__s}{$H_{\mathrm{s}}$}.
\item[extraData]\linkdest{block_extraData_H__x}{} An arbitrary byte array containing data relevant to this block. This must be 32 bytes or fewer; formally $H_{\mathrm{x}}$.
\item[mixHash]\linkdest{mixHash_H__m}{} A 256-bit hash which, combined with the nonce, proves that a sufficient amount of computation has been carried out on this block; formally $H_{\mathrm{m}}$.
\item[nonce]\linkdest{block_nonce_H__n}{} A 64-bit hash which, combined with the mix-hash, proves that a sufficient amount of computation has been carried out on this block; formally $H_{\mathrm{n}}$.
\end{description}

\linkdest{ommer_block_headers_B__U}{}\linkdest{block_B}{}The other two components in the block are simply a list of ommer block headers (of the same format as above) and a series of the transactions. Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (B_{H}, B_{\mathbf{T}}, B_{\mathbf{U}})
\end{equation}

@@

\hypertarget{self_destruct_set_wordy_defn_A__s}{}The tuple contents include $A_{\mathbf{s}}$, the self-destruct set: a set of accounts that will be discarded following the transaction's completion.\hypertarget{tx_log_series_wordy_defn_A__l}{} $A_{\mathbf{l}}$ is the log series: this is a series of archived and indexable `checkpoints' in VM code execution that allow for contract-calls to be easily tracked by onlookers external to the Ethereum world (such as decentralised application front-ends).\hypertarget{tx_touched_accounts_wordy_defn_A__t}{} $A_{\mathbf{t}}$ is the set of touched accounts, of which the empty ones are deleted at the end of a transaction.\hypertarget{refund_balance_defn_words_A__r}{} Finally there is $A_{\mathrm{r}}$, the refund balance, increased through using the \hyperlink{SSTORE}{{\small SSTORE}} instruction in order to reset contract storage to zero from some non-zero value. Though not immediately refunded, it is allowed to partially offset the total execution costs.

We define the empty substate $A^0$ to have no self-destructs, no logs, no touched accounts and a zero refund balance:
\begin{equation}
A^0 \equiv (\varnothing,(), \varnothing, 0)
\end{equation}

@@

After the message call or contract creation is processed, the state is finalised by determining the amount to be refunded, $g^*$ from the remaining gas, $g'$, plus some allowance from the refund counter, to the sender at the original rate.
\begin{equation}
g^* \equiv g' + \min \{ \Big\lfloor \dfrac{T_{\mathrm{g}} - g'}{2} \Big\rfloor, \hyperlink{refund_balance_defn_words_A__r}{A_{\mathrm{r}}} \}
\end{equation}

The total refundable amount is the legitimately remaining gas $g'$, added to \hyperlink{refund_balance_defn_words_A__r}{$A_{\mathrm{r}}$}, with the latter component being capped up to a maximum of half (rounded down) of the total amount used $T_{\mathrm{g}} - g'$.

@@

\hypertarget{tx_total_gas_used_Upsilon_pow_g}{}\hypertarget{tx_logs_Upsilon_pow_l}{}\hypertarget{tx_status_Upsilon_pow_z}{}And finally, we specify $\Upsilon^{\mathrm{g}}$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^{\mathrm{z}}$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^{\mathrm{g}}(\boldsymbol{\sigma}, T) & \equiv & T_{\mathrm{g}} - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & \hyperlink{tx_log_series_wordy_defn_A__l}{A_{\mathbf{l}}} \\
\Upsilon^{\mathrm{z}}(\boldsymbol{\sigma}, T) & \equiv & z
\end{eqnarray}

@@

The given \textbf{gasUsed} must correspond faithfully to the transactions listed: ${B_{H}}_{\mathrm{g}}$, the total gas used in the block, must be equal to the accumulated gas used according to the final transaction:
\begin{equation}
{B_{H}}_{\mathrm{g}} = \ell(\mathbf{R})_{\mathrm{u}}
\end{equation}

>>>>

\begin{description}
\item[parentHash]\linkdest{parent_Hash_H__p_def_words}{} The Keccak 256-bit hash of the parent block's header, in its entirety; formally $H_{\mathrm{p}}$.
\item[ommersHash] The Keccak 256-bit hash of the ommers list portion of this block; formally $H_{\mathrm{o}}$.
\item[beneficiary]\linkdest{beneficiary_H__c}{}\linkdest{H__c} The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_{\mathrm{c}}$.
\item[stateRoot] The Keccak 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_{\mathrm{r}}$.
\item[transactionsRoot] The Keccak 256-bit hash of the root node of the trie structure populated with each transaction in the transactions list portion of the block; formally $H_{\mathrm{t}}$.
\item[receiptsRoot]\linkdest{receipts_Root_def_words}{} The Keccak 256-bit hash of the root node of the trie structure populated with the receipts of each transaction in the transactions list portion of the block; formally $H_{\mathrm{e}}$.
\item[logsBloom]\linkdest{logs_Bloom_def_words}{} The Bloom filter composed from indexable information (logger address and log topics) contained in each log entry from the receipt of each transaction in the transactions list; formally $H_{\mathrm{b}}$.
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_{\mathrm{d}}$.
\item[number]\linkdest{block_number_word_def_H_i}{} A scalar value equal to the number of ancestor blocks. The genesis block has a number of zero; formally \hyperlink{block_number_H__i}{$H_{\mathrm{i}}$}.
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_{\mathrm{l}}$.
\item[gasUsed]\linkdest{block_gas_used_H__g}{}\linkdest{H__g} A scalar value equal to the total gas used in transactions in this block; formally $H_{\mathrm{g}}$.
\item[timestamp]\linkdest{block_timestamp_word_def_H__s}{} A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally \hyperlink{block_timestamp_H__s}{$H_{\mathrm{s}}$}.
\item[extraData]\linkdest{block_extraData_H__x}{} An arbitrary byte array containing data relevant to this block. This must be 32 bytes or fewer; formally $H_{\mathrm{x}}$.
\item[mixHash]\linkdest{mixHash_H__m}{} A 256-bit hash which, combined with the nonce, proves that a sufficient amount of computation has been carried out on this block; formally $H_{\mathrm{m}}$.
\item[nonce]\linkdest{block_nonce_H__n}{} A 64-bit hash which, combined with the mix-hash, proves that a sufficient amount of computation has been carried out on this block; formally $H_{\mathrm{n}}$.
\end{description}
\linkdest{ommer_block_headers_B__U}{}\linkdest{block_B}{}The other two components in the block are simply a list of ommer block headers (of the same format as above) and a series of the transactions. Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (B_{H}, B_{\mathbf{T}}, B_{\mathbf{U}})
\end{equation}

@@

\hypertarget{self_destruct_set_wordy_defn}{}The tuple contents include $A_{\mathbf{s}}$, the self-destruct set: a set of accounts that will be discarded following the transaction's completion.\hypertarget{tx_log_series_wordy_defn}{} $A_{\mathbf{l}}$ is the log series: this is a series of archived and indexable `checkpoints' in VM code execution that allow for contract-calls to be easily tracked by onlookers external to the Ethereum world (such as decentralised application front-ends).\hypertarget{tx_touched_accounts_wordy_defn}{} $A_{\mathbf{t}}$ is the set of touched accounts, of which the empty ones are deleted at the end of a transaction.\hypertarget{refund_balance_defn_words}{} Finally there is $A_{\mathrm{r}}$, the refund balance, increased through using the \hyperlink{SSTORE}{{\small SSTORE}} instruction in order to reset contract storage to zero from some non-zero value. Though not immediately refunded, it is allowed to partially offset the total execution costs.

We define the empty substate $A^0$ to have no self-destructs, no logs, no touched accounts and a zero refund balance:
\begin{equation}
A^0 \equiv (\varnothing, (), \varnothing, 0)
\end{equation}

@@

After the message call or contract creation is processed, the state is finalised by determining the amount to be refunded, $g^*$ from the remaining gas, $g'$, plus some allowance from the refund counter, to the sender at the original rate.
\begin{equation}
g^* \equiv g' + \min \{ \Big\lfloor \dfrac{T_{\mathrm{g}} - g'}{2} \Big\rfloor, A_{\mathrm{r}} \}
\end{equation}

The total refundable amount is the legitimately remaining gas $g'$, added to $A_{\mathrm{r}}$, with the latter component being capped up to a maximum of half (rounded down) of the total amount used $T_{\mathrm{g}} - g'$.

@@

\hypertarget{tx_total_gas_used_Upsilon_pow_g}{}\hypertarget{tx_logs_Upsilon_pow_l}{}\hypertarget{tx_status_Upsilon_pow_z}{}And finally, we specify $\Upsilon^{\mathrm{g}}$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^{\mathrm{z}}$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^{\mathrm{g}}(\boldsymbol{\sigma}, T) & \equiv & T_{\mathrm{g}} - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & A_{\mathbf{l}} \\
\Upsilon^{\mathrm{z}}(\boldsymbol{\sigma}, T) & \equiv & z
\end{eqnarray}

@@

The given \textbf{gasUsed} must correspond faithfully to the transactions listed: \hyperlink{H__g}{${B_{H}}_{\mathrm{g}}$}, the total gas used in the block, must be equal to the accumulated gas used according to the final transaction:
\begin{equation}
{B_{H}}_{\mathrm{g}} = \hyperlink{ell}{\ell}(\hyperlink{R__u}{\mathbf{R})_{\mathrm{u}}}
\end{equation}
